---
title: "Santander"
author: "Rodrigo Rivera"
date: "January 10, 2017"
output: html_document
---
#Competition Details
Under their current system, a small number of Santander’s customers receive many recommendations while many others rarely see any resulting in an uneven customer experience. In their second competition, Santander is challenging Kagglers to predict which products their existing customers will use in the next month based on their past behavior and that of similar customers.

With a more effective recommendation system in place, Santander can better meet the individual needs of all customers and ensure their satisfaction no matter where they are in life.

Disclaimer: This data set does not include any real Santander Spain's customer, and thus it is not representative of Spain's customer base. 

#Data Information
In this competition, you are provided with 1.5 years of customers behavior data from Santander bank to predict what new products customers will purchase. The data starts at 2015-01-28 and has monthly records of products a customer has, such as "credit card", "savings account", etc. You will predict what additional products a customer will get in the last month, 2016-06-28, in addition to what they already have at 2016-05-28. These products are the columns named: ind_(xyz)_ult1, which are the columns #25 - #48 in the training data. You will predict what a customer will buy in addition to what they already had at 2016-05-28. 

The test and train sets are split by time, and public and private leaderboard sets are split randomly.

Please note: This sample does not include any real Santander Spain customers, and thus it is not representative of Spain's customer base. 

#Procesando la Data
Cargando librerías necesarias
```{r lib, cache = TRUE}
setwd("~/Desktop/Business/Kaggle/Santander")
library(AppliedPredictiveModeling)
library(caret)
library(ElemStatLearn)
library(pgmm)
library(rpart)
library(gbm)
library(lubridate)
library(forecast)
library(e1071)
library(randomForest)
library(dplyr)
```


Leyendo y Preprocesando la Data
```{r data, cache = TRUE}
train <- read.csv("train_ver2.csv")
names(train)
sapply(train, class)
train[train$ind_empleado == "", 3] = "N"
train <- train[complete.cases(train$pais_residencia), ] #13619575
train[train$sexo == "", 5] = NA
train <- train[complete.cases(train$sexo), ] #13619505
train <- train[complete.cases(train$tiprel_1mes), ]
train[train$conyuemp == "", 3] = "N"
train <- train[complete.cases(train$canal_entrada), ]
train <- train[complete.cases(train$renta), ]
train <- mutate(train, wday = wday(fecha_dato, label = TRUE))
train <- mutate(train, antiguedad = as.numeric(difftime(as.Date(fecha_dato), as.Date(fecha_alta), units="days")))
dim(train)
quantile(train$renta, na.rm = T)
train <- mutate(train, claseRenta = renta)
train[, 50] = 1 #medio
train[train$renta < quantile(train$renta)[2], 50] = 0 #bajo
train[train$renta > quantile(train$renta)[4], 50] = 2 #alto
table(train$claseRenta)
#View(head(train))
df <- train[train$ncodpers == 1375586, ]
#View(df)

#Decidiendo que variables predecir (si muestran NZV -near zero variance- no tiene sentido predecirlas)
(table(train$ind_ahor_fin_ult1))/length(train$fecha_dato) #no
(table(train$ind_aval_fin_ult1))/length(train$fecha_dato) #no
(table(train$ind_cco_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_cder_fin_ult1))/length(train$fecha_dato) #no
(table(train$ind_cno_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_ctju_fin_ult1))/length(train$fecha_dato) #quizas
(table(train$ind_ctma_fin_ult1))/length(train$fecha_dato) #no
(table(train$ind_ctop_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_ctpp_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_deco_fin_ult1))/length(train$fecha_dato) #no
(table(train$ind_deme_fin_ult1))/length(train$fecha_dato) #no
(table(train$ind_dela_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_ecue_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_fond_fin_ult1))/length(train$fecha_dato) #quizas
(table(train$ind_hip_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_plan_fin_ult1))/length(train$fecha_dato) #quizas
(table(train$ind_pres_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_reca_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_tjcr_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_valo_fin_ult1))/length(train$fecha_dato) #si
(table(train$ind_viv_fin_ult1))/length(train$fecha_dato) #no
(table(train$ind_nomina_ult1))/length(train$fecha_dato) #si
(table(train$ind_nom_pens_ult1))/length(train$fecha_dato) #si
(table(train$ind_recibo_ult1))/length(train$fecha_dato) #si

#Pasando a factor los 'y'
train$ind_cco_fin_ult1 <- as.factor(train$ind_cco_fin_ult1)
train$ind_cno_fin_ult1 <- as.factor(train$ind_cno_fin_ult1)
train$ind_ctop_fin_ult1 <- as.factor(train$ind_ctop_fin_ult1)
train$ind_ctpp_fin_ult1 <- as.factor(train$ind_ctpp_fin_ult1)
train$ind_dela_fin_ult1 <- as.factor(train$ind_dela_fin_ult1)
train$ind_ecue_fin_ult1 <- as.factor(train$ind_ecue_fin_ult1)
train$ind_hip_fin_ult1 <- as.factor(train$ind_hip_fin_ult1)
train$ind_pres_fin_ult1 <- as.factor(train$ind_pres_fin_ult1)
train$ind_reca_fin_ult1 <- as.factor(train$ind_reca_fin_ult1)
train$ind_tjcr_fin_ult1 <- as.factor(train$ind_tjcr_fin_ult1)
train$ind_valo_fin_ult1 <- as.factor(train$ind_valo_fin_ult1)
train$ind_nomina_ult1 <- as.factor(train$ind_nomina_ult1)
train$wday <- as.numeric(train$wday)
train$claseRenta <- as.factor(train$claseRenta)
train$ind_actividad_cliente <- as.factor(train$ind_actividad_cliente)
train$age <- as.numeric(train$age)
sapply(train, class)
```

```{r, echo = FALSE}
#dividiendo la data
x <- 1000
traina <- train[1:x,]
```

```{r partition, cache = TRUE}
inTrain <- createDataPartition(y=traina$ind_cco_fin_ult1, p=0.7, list=FALSE)
straininga <- traina[inTrain,]
```

#Modelo
Escogiendo el mejor modelo para cada variable en base al accuracy.
```{r regs, cache = TRUE}
set.seed(502)
#CCO
ctop <- train[train$ind_cco_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_cco_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_cco_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestacco <- traina2[-inTrain,]
#RF
system.time(fit1cco <- train(ind_cco_fin_ult1 ~ ind_empleado + pais_residencia + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1cco <- predict(fit1cco, stestacco)
table(pred1cco)
confusionMatrix(pred1cco, stestacco$ind_cco_fin_ult1)
confusionMatrix(pred1cco, stestacco$ind_cco_fin_ult1)$overall[1] #92%
#GBM
system.time(fit2cco <- train(ind_cco_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2cco <- predict(fit2cco, stestacco)
table(pred2cco)
confusionMatrix(pred2cco, stestacco$ind_cco_fin_ult1)
confusionMatrix(pred2cco, stestacco$ind_cco_fin_ult1)$overall[1] #94.6%
#GLM
system.time(fit3cco <- train(ind_cco_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3cco <- predict(fit3cco, stestacco)
table(pred3cco)
confusionMatrix(pred3cco, stestacco$ind_cco_fin_ult1)
confusionMatrix(pred3cco, stestacco$ind_cco_fin_ult1)$overall[1] #92.33%
#Promedio
ccoprom <- (as.numeric(pred2cco) + as.numeric(pred1cco) + as.numeric(pred3cco) - 3)/3
ccoprom <- round(ccoprom)
table(ccoprom)
confusionMatrix(ccoprom, stestacco$ind_cco_fin_ult1)$overall[1] #92%


#cno
ctop <- train[train$ind_cno_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_cno_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_cno_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestacno <- traina2[-inTrain,]
#RF
system.time(fit1cno <- train(ind_cno_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1cno <- predict(fit1cno, stestacno)
table(pred1cno)
confusionMatrix(pred1cno, stestacno$ind_cno_fin_ult1)
confusionMatrix(pred1cno, stestacno$ind_cno_fin_ult1)$overall[1] #94.3%
#GBM
system.time(fit2cno <- train(ind_cno_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2cno <- predict(fit2cno, stestacno)
table(pred2cno)
confusionMatrix(pred2cno, stestacno$ind_cno_fin_ult1)
confusionMatrix(pred2cno, stestacno$ind_cno_fin_ult1)$overall[1] #94.3%
#GLM
system.time(fit3cno <- train(ind_cno_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3cno <- predict(fit3cno, stestacno)
table(pred3cno)
confusionMatrix(pred3cno, stestacno$ind_cno_fin_ult1)
confusionMatrix(pred3cno, stestacno$ind_cno_fin_ult1)$overall[1] #70.2%
#Promedio
cnoprom <- (as.numeric(pred2cno) + as.numeric(pred1cno) + as.numeric(pred3cno) - 3)/3
cnoprom <- round(cnoprom)
table(cnoprom)
confusionMatrix(cnoprom, stestacno$ind_cno_fin_ult1)$overall[1] #94.6%



#ctop
ctop <- train[train$ind_ctop_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_ctop_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_ctop_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestactop <- traina2[-inTrain,]
#RF
system.time(fit1ctop <- train(ind_ctop_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1ctop <- predict(fit1ctop, stestactop)
table(pred1ctop)
confusionMatrix(pred1ctop, stestactop$ind_ctop_fin_ult1)
confusionMatrix(pred1ctop, stestactop$ind_ctop_fin_ult1)$overall[1] #100%
#GBM
system.time(fit2ctop <- train(ind_ctop_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2ctop <- predict(fit2ctop, stestactop)
table(pred2ctop)
confusionMatrix(pred2ctop, stestactop$ind_ctop_fin_ult1)
confusionMatrix(pred2ctop, stestactop$ind_ctop_fin_ult1)$overall[1] #100%
#GLM
system.time(fit3ctop <- train(ind_ctop_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3ctop <- predict(fit3ctop, stestactop)
table(pred3ctop)
confusionMatrix(pred3ctop, stestactop$ind_ctop_fin_ult1)
confusionMatrix(pred3ctop, stestactop$ind_ctop_fin_ult1)$overall[1] #93.3%
#Promedio
ctopprom <- (as.numeric(pred2ctop) + as.numeric(pred1ctop) + as.numeric(pred3ctop) - 3)/3
ctopprom <- round(ctopprom)
table(ctopprom)
confusionMatrix(ctopprom, stestactop$ind_ctop_fin_ult1)$overall[1] #100%



#ctpp
ctop <- train[train$ind_ctpp_fin_ult1 == 1, ]
ctop <- ctop[1:500, ]
ctop <- rbind(ctop, train[1:500, ])
traina2 <- ctop
table(traina2$ind_ctpp_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_ctpp_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestactpp <- traina2[-inTrain,]
#RF
system.time(fit1ctpp <- train(ind_ctpp_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1ctpp <- predict(fit1ctpp, stestactpp)
table(pred1ctpp)
confusionMatrix(pred1ctpp, stestactpp$ind_ctpp_fin_ult1)
confusionMatrix(pred1ctpp, stestactpp$ind_ctpp_fin_ult1)$overall[1] #100%
#GBM
system.time(fit2ctpp <- train(ind_ctpp_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2ctpp <- predict(fit2ctpp, stestactpp)
table(pred2ctpp)
confusionMatrix(pred2ctpp, stestactpp$ind_ctpp_fin_ult1)
confusionMatrix(pred2ctpp, stestactpp$ind_ctpp_fin_ult1)$overall[1] #100%
#GLM
system.time(fit3ctpp <- train(ind_ctpp_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3ctpp <- predict(fit3ctpp, stestactpp)
table(pred3ctpp)
confusionMatrix(pred3ctpp, stestactpp$ind_ctpp_fin_ult1)
confusionMatrix(pred3ctpp, stestactpp$ind_ctpp_fin_ult1)$overall[1] #100%
#Promedio
ctppprom <- (as.numeric(pred2ctpp) + as.numeric(pred1ctpp) + as.numeric(pred3ctpp) - 3)/3
ctppprom <- round(ctppprom)
table(ctppprom)
confusionMatrix(ctppprom, stestactpp$ind_ctpp_fin_ult1)$overall[1] #100%



#dela
ctop <- train[train$ind_dela_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_dela_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_dela_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestadela <- traina[-inTrain,]
#RF
system.time(fit1dela <- train(ind_dela_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1dela <- predict(fit1dela, stestadela)
table(pred1dela)
confusionMatrix(pred1dela, stestadela$ind_dela_fin_ult1)
confusionMatrix(pred1dela, stestadela$ind_dela_fin_ult1)$overall[1] #98.6%
#GBM
system.time(fit2dela <- train(ind_dela_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2dela <- predict(fit2dela, stestadela)
table(pred2dela)
confusionMatrix(pred2dela, stestadela$ind_dela_fin_ult1)
confusionMatrix(pred2dela, stestadela$ind_dela_fin_ult1)$overall[1] #98.3%
#GLM
system.time(fit3dela <- train(ind_dela_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3dela <- predict(fit3dela, stestadela)
table(pred3dela)
confusionMatrix(pred3dela, stestadela$ind_dela_fin_ult1)
confusionMatrix(pred3dela, stestadela$ind_dela_fin_ult1)$overall[1] #92.6%
#Promedio
delaprom <- (as.numeric(pred2dela) + as.numeric(pred1dela) + as.numeric(pred3dela) - 3)/3
delaprom <- round(delaprom)
table(delaprom)
confusionMatrix(delaprom, stestadela$ind_dela_fin_ult1)$overall[1] #98.3%



#ecue
ctop <- train[train$ind_ecue_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_ecue_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_ecue_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestaecue <- traina[-inTrain,]
#RF
system.time(fit1ecue <- train(ind_ecue_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1ecue <- predict(fit1ecue, stestaecue)
table(pred1ecue)
confusionMatrix(pred1ecue, stestaecue$ind_ecue_fin_ult1)
confusionMatrix(pred1ecue, stestaecue$ind_ecue_fin_ult1)$overall[1] #92.98%
#GBM
system.time(fit2ecue <- train(ind_ecue_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2ecue <- predict(fit2ecue, stestaecue)
table(pred2ecue)
confusionMatrix(pred2ecue, stestaecue$ind_ecue_fin_ult1)
confusionMatrix(pred2ecue, stestaecue$ind_ecue_fin_ult1)$overall[1] #89.3%
#GLM
system.time(fit3ecue <- train(ind_ecue_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3ecue <- predict(fit3ecue, stestaecue)
table(pred3ecue)
confusionMatrix(pred3ecue, stestaecue$ind_ecue_fin_ult1)
confusionMatrix(pred3ecue, stestaecue$ind_ecue_fin_ult1)$overall[1] #91.97%
#Promedio
ecueprom <- (as.numeric(pred2ecue) + as.numeric(pred1ecue) + as.numeric(pred3ecue) - 3)/3
ecueprom <- round(ecueprom)
table(ecueprom)
confusionMatrix(ecueprom, stestaecue$ind_ecue_fin_ult1)$overall[1] #91.97%



#hip
ctop <- train[train$ind_hip_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_hip_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_hip_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestahip <- traina2[-inTrain,]
#RF
system.time(fit1hip <- train(ind_hip_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1hip <- predict(fit1hip, stestahip)
table(pred1hip)
confusionMatrix(pred1hip, stestahip$ind_hip_fin_ult1)
confusionMatrix(pred1hip, stestahip$ind_hip_fin_ult1)$overall[1] #99.5%
#GBM
system.time(fit2hip <- train(ind_hip_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2hip <- predict(fit2hip, stestahip)
table(pred2hip)
confusionMatrix(pred2hip, stestahip$ind_hip_fin_ult1)
confusionMatrix(pred2hip, stestahip$ind_hip_fin_ult1)$overall[1] #99.3%
#GLM
system.time(fit3hip <- train(ind_hip_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3hip <- predict(fit3hip, stestahip)
table(pred3hip)
confusionMatrix(pred3hip, stestahip$ind_hip_fin_ult1)
confusionMatrix(pred3hip, stestahip$ind_hip_fin_ult1)$overall[1] #95.67%
#Promedio
hipprom <- (as.numeric(pred2hip) + as.numeric(pred1hip) + as.numeric(pred3hip) - 3)/3
hipprom <- round(hipprom)
table(hipprom)
confusionMatrix(hipprom, stestahip$ind_hip_fin_ult1)$overall[1] #99.5%



#pres
ctop <- train[train$ind_pres_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_pres_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_pres_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestapres <- traina2[-inTrain,]
#RF
system.time(fit1pres <- train(ind_pres_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1pres <- predict(fit1pres, stestapres)
table(pred1pres)
confusionMatrix(pred1pres, stestapres$ind_pres_fin_ult1)
confusionMatrix(pred1pres, stestapres$ind_pres_fin_ult1)$overall[1] #98.7%
#GBM
system.time(fit2pres <- train(ind_pres_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2pres <- predict(fit2pres, stestapres)
table(pred2pres)
confusionMatrix(pred2pres, stestapres$ind_pres_fin_ult1)
confusionMatrix(pred2pres, stestapres$ind_pres_fin_ult1)$overall[1] #99.3%
#GLM
system.time(fit3pres <- train(ind_pres_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3pres <- predict(fit3pres, stestapres)
table(pred3pres)
confusionMatrix(pred3pres, stestapres$ind_pres_fin_ult1)
confusionMatrix(pred3pres, stestapres$ind_pres_fin_ult1)$overall[1] #94.3%
#Promedio
presprom <- (as.numeric(pred2pres) + as.numeric(pred1pres) + as.numeric(pred3pres) - 3)/3
presprom <- round(presprom)
table(presprom)
confusionMatrix(presprom, stestapres$ind_pres_fin_ult1)$overall[1] #99.7%



#reca
ctop <- train[train$ind_reca_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_reca_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_reca_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestareca <- traina2[-inTrain,]
#RF
system.time(fit1reca <- train(ind_reca_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1reca <- predict(fit1reca, stestareca)
table(pred1reca)
confusionMatrix(pred1reca, stestareca$ind_reca_fin_ult1)
confusionMatrix(pred1reca, stestareca$ind_reca_fin_ult1)$overall[1] #97.7%
#GBM
system.time(fit2reca <- train(ind_reca_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2reca <- predict(fit2reca, stestareca)
table(pred2reca)
confusionMatrix(pred2reca, stestareca$ind_reca_fin_ult1)
confusionMatrix(pred2reca, stestareca$ind_reca_fin_ult1)$overall[1] #96.99%
#GLM
system.time(fit3reca <- train(ind_reca_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3reca <- predict(fit3reca, stestareca)
table(pred3reca)
confusionMatrix(pred3reca, stestareca$ind_reca_fin_ult1)
confusionMatrix(pred3reca, stestareca$ind_reca_fin_ult1)$overall[1] #82%
#Promedio
recaprom <- (as.numeric(pred2reca) + as.numeric(pred1reca)-2)/3
recaprom <- round(recaprom)
table(recaprom)
confusionMatrix(recaprom, stestareca$ind_reca_fin_ult1)$overall[1] #96.99%



#tjcr
ctop <- train[train$ind_tjcr_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_tjcr_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_tjcr_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestatjcr <- traina2[-inTrain,]
#RF
system.time(fit1tjcr <- train(ind_tjcr_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1tjcr <- predict(fit1tjcr, stestatjcr)
table(pred1tjcr)
confusionMatrix(pred1tjcr, stestatjcr$ind_tjcr_fin_ult1)
confusionMatrix(pred1tjcr, stestatjcr$ind_tjcr_fin_ult1)$overall[1] #98.66%
#GBM
system.time(fit2tjcr <- train(ind_tjcr_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2tjcr <- predict(fit2tjcr, stestatjcr)
table(pred2tjcr)
confusionMatrix(pred2tjcr, stestatjcr$ind_tjcr_fin_ult1)
confusionMatrix(pred2tjcr, stestatjcr$ind_tjcr_fin_ult1)$overall[1] #97.99%
#GLM
system.time(fit3tjcr <- train(ind_tjcr_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3tjcr <- predict(fit3tjcr, stestatjcr)
table(pred3tjcr)
confusionMatrix(pred3tjcr, stestatjcr$ind_tjcr_fin_ult1)
confusionMatrix(pred3tjcr, stestatjcr$ind_tjcr_fin_ult1)$overall[1] #84.6%
#Promedio
tjcrprom <- (as.numeric(pred2tjcr) + as.numeric(pred1tjcr) + as.numeric(pred3tjcr) - 3)/3
tjcrprom <- round(tjcrprom)
table(tjcrprom)
confusionMatrix(tjcrprom, stestatjcr$ind_tjcr_fin_ult1)$overall[1] #98.3%



#valo
ctop <- train[train$ind_valo_fin_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_valo_fin_ult1)
inTrain <- createDataPartition(y=traina2$ind_valo_fin_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestavalo <- traina2[-inTrain,]
#RF
system.time(fit1valo <- train(ind_valo_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1valo <- predict(fit1valo, stestavalo)
table(pred1valo)
confusionMatrix(pred1valo, stestavalo$ind_valo_fin_ult1)
confusionMatrix(pred1valo, stestavalo$ind_valo_fin_ult1)$overall[1] #98.7%
#GBM
system.time(fit2valo <- train(ind_valo_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2valo <- predict(fit2valo, stestavalo)
table(pred2valo)
confusionMatrix(pred2valo, stestavalo$ind_valo_fin_ult1)
confusionMatrix(pred2valo, stestavalo$ind_valo_fin_ult1)$overall[1] #98.3%
#GLM
system.time(fit3valo <- train(ind_valo_fin_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3valo <- predict(fit3valo, stestavalo)
table(pred3valo)
confusionMatrix(pred3valo, stestavalo$ind_valo_fin_ult1)
confusionMatrix(pred3valo, stestavalo$ind_valo_fin_ult1)$overall[1] #84.9%
#Promedio
valoprom <- (as.numeric(pred2valo) + as.numeric(pred1valo) + as.numeric(pred3valo) - 3)/3
valoprom <- round(valoprom)
table(valoprom)
confusionMatrix(valoprom, stestavalo$ind_valo_fin_ult1)$overall[1] #98.3%



#nomina
ctop <- train[train$ind_nomina_ult1 == 1, ]
ctop <- ctop[1:250, ]
ctop <- rbind(ctop, train[1:750, ])
traina2 <- ctop
table(traina2$ind_nomina_ult1)
inTrain <- createDataPartition(y=traina2$ind_nomina_ult1, p=0.7, list=FALSE)
straininga <- traina2[inTrain,]
stestanomina <- traina[-inTrain,]
#RF
system.time(fit1nomina <- train(ind_nomina_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "rf"))
pred1nomina <- predict(fit1nomina, stestanomina)
table(pred1nomina)
confusionMatrix(pred1nomina, stestanomina$ind_nomina_ult1)
confusionMatrix(pred1nomina, stestanomina$ind_nomina_ult1)$overall[1] #99.31%
#GBM
system.time(fit2nomina <- train(ind_nomina_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "gbm"))
pred2nomina <- predict(fit2nomina, stestanomina)
table(pred2nomina)
confusionMatrix(pred2nomina, stestanomina$ind_nomina_ult1)
confusionMatrix(pred2nomina, stestanomina$ind_nomina_ult1)$overall[1] #97.9%
#GLM
system.time(fit3nomina <- train(ind_nomina_ult1 ~ ind_empleado + sexo + age + antiguedad + indrel_1mes + conyuemp + canal_entrada + ind_actividad_cliente + claseRenta + segmento, data=straininga, method= "glm"))
pred3nomina <- predict(fit3nomina, stestanomina)
table(pred3nomina)
confusionMatrix(pred3nomina, stestanomina$ind_nomina_ult1)
confusionMatrix(pred3nomina, stestanomina$ind_nomina_ult1)$overall[1] #91.6%
#Promedio
nominaprom <- (as.numeric(pred2nomina) + as.numeric(pred1nomina) + as.numeric(pred3nomina) - 3)/3
nominaprom <- round(nominaprom)
table(nominaprom)
confusionMatrix(nominaprom, stestanomina$ind_nomina_ult1)$overall[1] #98.7%
```



#Test Set
Leyendo y pre procesando el test set
```{r test, cache = TRUE}
test <- read.csv("test_ver2.csv")
test <- mutate(test, antiguedad = as.numeric(difftime(as.Date(fecha_dato), as.Date(fecha_alta), units="days")))
test$renta <- as.numeric(test$renta)
test[test$renta == 1, 23] = mean(test$renta, na.rm=TRUE)
test <- mutate(test, claseRenta = renta)
test[, 25] = 1 #medio
q <- quantile(as.numeric(train$renta))
test[test$renta < q[2], 25] = 0 #bajo
test[test$renta > q[4], 25] = 2 #alto
table(test$claseRenta)
#View(head(test))
test$claseRenta <- as.factor(test$claseRenta)
test$ind_actividad_cliente <- as.factor(test$ind_actividad_cliente)
test$age <- as.numeric(test$age)
test$indrel_1mes <- as.factor(test$indrel_1mes)
sapply(test, class)
test <- select(test, ind_empleado, ncodpers, pais_residencia, sexo, age, antiguedad, indrel_1mes, conyuemp, canal_entrada, ind_actividad_cliente, claseRenta, segmento)
dim(test)
test[is.na(test[7]), 7] <- 1
test[is.na(test[8]), 8] <- "N"
table(is.na(test[11]))
```

Predicciones
```{r pred, cache = TRUE}
#CCO
#GLM
cco <- predict(fit2cco, test)

#cno
#RF
cno1 <- predict(fit1cno, test)
#GBM
cno2 <- predict(fit2cno, test)
#GLM
cno3 <- predict(fit3cno, test)
#Promedio
cno <- (as.numeric(cno1) + as.numeric(cno2) + as.numeric(cno3) - 3)/3
cno <- round(cnoprom)

#ctop
#RF
ctop <- predict(fit1ctop, test)

#ctpp
#RF
ctpp <- predict(fit1ctpp, test)

#dela
#RF
dela <- predict(fit1dela, test)

#ecue
#RF
ecue <- predict(fit1ecue, test)

#hip
#RF
hip <- predict(fit1hip, test)

#pres
#RF
pres1 <- predict(fit1pres, test)
#GBM
pres2 <- predict(fit2pres, test)
#GLM
pres3 <- predict(fit3pres, test)
#Promedio
pres <- (as.numeric(pres1) + as.numeric(pres2) + as.numeric(pres3) - 3)/3
pres <- round(presprom)

#reca
#RF
reca <- predict(fit1reca, test)

#tjcr
#RF
tjcr <- predict(fit1tjcr, test)

#valo
#RF
valo <- predict(fit2valo, test)

#nomina
#RF
nomina <- predict(fit1nomina, test)

#final
final <- cbind(cco, ctop, cno1, ctpp, dela, ecue, hip, pres3, reca, tjcr, valo, nomina)
final <- as.data.frame(final)
final <- cbind(final, test$ncodpers)
dim(final)
final[,1:12] <- final[,1:12] -1
View(final)
```























